Flexibility of interactions depends on habitat suitability

### 2019-07-21 paper/manuscript.Rmd
Explain sensitivity analysis in manuscript

Next, we overlapped the occurrence and our environmental rasters such that each occurrence location is characterized by a vector with information of our 37 bioclimatic and topographic variables . 
If a species had more than one occurrence records within one of the cells of the bioclimatic raster we only included one of the occurrence records. 
We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrrence records collected opportunistically as the ones we use here. 
Overall we removed `r scales::percent(percent_thinned)` of the occurrences which resulted in a total of `r round(sum(n_thinned_occurrences$N)/1000000, digits = 1)` million occurrences used in our niche analysis. 
A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not exactly match the land mass boundaries. 
The result of this missmatch is that at least one of the environmental variables was not available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total). 
As expected a vast majority of these cells were close to the shore. 
To address this issue, calculated average value of environmental variables within a `r config$climate_buffer/1000`km buffer of the center of the cell where the variable is missing, and used it to approximate the value of the variable in that cell. 
In this fashion we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells were they were missing. 
To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but using a `r config$climate_buffer*2/1000`km buffer.

@@

To determine the environmental space of each species we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation. 
We then estimate a kernel density function to determine a smooth density of occurrences in the environmenta space. 
The main advantage of using a kernel smoother is that it reduces the sensitivity of the niche to sampling effort and the resolution chosen for the environmental space grid [@broennimann_measuring_2012]. 
To calculate the kernel we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@ecospat_citation] with a grid resolution of 200.
We normalise the occurrence density such that our suitability ranges beetween 1 for the grids with environmental conditions in which the species was most commonly observed and 0 for the grids in which it was never observed.  
We then determine the location in environmental space of the plant-pollinator communities where the species is present using the function `suprow` from `ade4` and calculate its corresponding suitability using the R package `raster` `r as.character(packageVersion('raster'))` [@raster_citation].

We removed from further analyis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.

>>>>

Next, we overlapped the occurrence and our environmental rasters such that each occurrence location is characterized by a vector with information of our 37 bioclimatic and topographic variables . 
If a species had more than one occurrence records within one of the cells of the bioclimatic raster we only included one of the occurrence records. 
We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrrence records collected opportunistically as the ones we use here. 
Overall we removed `r scales::percent(percent_thinned)` of the occurrences which resulted in a total of `r round(sum(n_thinned_occurrences$N)/1000000, digits = 1)` million occurrences used in our niche analysis. 
A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not exactly match the land mass boundaries. 
The result of this missmatch is that at least one of the environmental variables was not available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total). 
As expected a vast majority of these cells were close to the shore. 
To address this issue, calculated average value of environmental variables within a `r config$climate_buffer/1000`km buffer of the center of the cell where the variable is missing, and used it to approximate the value of the variable in that cell. 
In this fashion we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells were they were missing. 
To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but using a `r config$climate_buffer*2/1000`km buffer. 
We removed from further analyis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.

@@

To determine the environmental space we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation. 
We then determine the position of species occurrences in the environmental space and estimate their bivariate density distribution using the kernel method. 
The main advantage of using the kernel method is that it reduces the sensitivity of the niche to sampling effort and the resolution chosen for the environmental space grid [@broennimann_measuring_2012]. 
To calculate the kernel we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@ecospat_citation] with a grid resolution of 200.
We then normalise the occurrence density distribution such that our suitability ranges beetween 1 for the grids with environmental conditions in which the species was most commonly observed and 0 for the grids in which it was never observed.  
We then determine the location in environmental space of the plant-pollinator communities where the species is present using the function `suprow` from `ade4` and calculate its corresponding suitability using the R package `raster` `r as.character(packageVersion('raster'))` [@raster_citation].

```{r sensitivity-analysis-calculations}
loadd(sensitivity_species_name, n_enough_occurrences)
n_occ_sensitivity_species <- n_thinned_occurrences %>%
  dplyr::filter(org_id == sensitivity_species_name$org_id[1]) %$% N

n_spp_not_enough_occ <- nrow(n_thinned_occurrences) - nrow(n_enough_occurrences)
```

We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental suitability values in our communities. 
For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =","`  occurrences available from GBIF. 
We found that, when we calculate the environmental space independently for each sepecies, we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.

```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = "asd"}
readd(fig_sensitivity_analysis)
```
